\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-06-19 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Start updating Results Section 4.2

>>>>

\medskip
Two further numerical simulations were performed in slightly modified test-cases (see Fig.~\ref{fem_cv_represent_a}) to assess model behaviour under distinct viscosity ratio conditions. In both simulations initial and boundary conditions remain the same, but V, but in this set of simulations the geometrical aspect ration is $2$ is following. The model was also qualitatively validated against laboratory experiments conducted by \citet{evans_1994}. The last set of simulations as this is described in fig.\ref{fem_cv_represent_a}c is and extension of the previous case and the aim of is to verify the behaviour of the flow for two different mobility ratios of $1$ and $10$ respectively.

### 2017-06-19 Papers/ViscousInstabilities/article_figure1.tex
Start updating Results Section 4.2

%%%
%%% FIGURE
%%%
\begin{landscape}
  \begin{figure}[ht]
    \vbox{ 
      \hbox{\includegraphics[width=.55\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.pdf}
            \includegraphics[width=.55\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} 
            \includegraphics[width=.55\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} }
      \hbox{\hspace{10cm} (a) VR = 1}
      \vspace{1cm}
      \hbox{\includegraphics[width=.55\textwidth]{./Pics1/mr10_fixed/mr10_fixed_100_1.pdf}
            \includegraphics[width=.55\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}
            \includegraphics[width=.55\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf} }
      \hbox{\hspace{10cm} (b) VR = 10  }}
\caption{Initial model validation: snapshots of numerical simulations performed with VR=1 and VR=10 (the domain contains \red{XX} elements).}
\label{fem_cv_represent_a}
\end{figure}
\end{landscape}
\clearpage
%%%
%%%
%%%

>>>>

%%%
%%% FIGURE
%%%
\begin{landscape}
  \begin{figure}[ht]
    \vbox{ 
      \hbox{\includegraphics[width=.55\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.pdf}
            \includegraphics[width=.55\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} 
            \includegraphics[width=.55\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} }
      \hbox{\hspace{10cm} (a) VR = 1}
      \vspace{1cm}
      \hbox{\includegraphics[width=.55\textwidth]{./Pics1/mr10_fixed/mr10_fixed_100_1.pdf}
            \includegraphics[width=.55\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}
            \includegraphics[width=.55\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf} }
      \hbox{\hspace{10cm} (b) VR = 10  }}
\caption{Initial model validation: snapshots of numerical simulations performed with VR=1 and VR=10 (the domain contains \red{XX} elements). \red{(It is clear that figures are not correct ... as they seem wrong.)}}
\label{fem_cv_represent_a}
\end{figure}
\end{landscape}
\clearpage
%%%
%%%
%%%
